Mahotas: Open source software for scriptable computer vision

### 2013-04-23 paper.tex
MIN C++ compiler is needed. Update downloads
The download number is not yet at 50k, but close enough that it will
surely pass that mark before the paper is final.

@@

Mahotas has been available in the Python Package Index since April~2010 and has
been downloaded over 40,000~times. This does not include any downloads from
other sources. Mahotas includes a full test suite. There are no known bugs.

>>>>

For compiling from source, a \cpp{} compiler is needed, as well as the
development headers for Python and numpy.

@@

Mahotas has been available in the Python Package Index since April~2010 and has
been downloaded over fifty thousand~times. This does not include any downloads
from other sources. Mahotas includes a full test suite. There are no known
bugs.
